An investigation into using scagnostics to find interesting projections of high-dimensional data

### 2018-10-10 scagnostics.Rmd
Compare final view for 3 different index functions.

@@

```{r bbhGuided, results="hide", fig.cap="Final view identified optimising the TIC index for the posterior obtained in the BBH merger simulation study."}
bbhM <- rescale(select(bbhD,-m2))
if(!file.exists("cache/bbhGuided.rda")){
  bbhTour <- save_history(bbhM, guided_tour(mineIndex("TIC")))
  bbhTourFull <- as.list(interpolate(bbhTour))
  save(bbhTour, bbhTourFull, file = "cache/bbhGuided.rda")
} else {
  load("cache/bbhGuided.rda")
}
iLast <- length(bbhTourFull)
fProj <- bbhTourFull[[iLast]]
dProj <- as.tibble(bbhM %*% fProj)
ggplot(dProj, aes(V1,V2)) + geom_point() + theme(aspect.ratio=1)
```

>>>>

invConvexIndex <- function(){
  function(mat){
    sR <- scagnostics.default(mat[,1],mat[,2])$s
    return(1 - sR["Convex"])
  }
}

@@

```{r bbhGuided, results="hide", fig.cap="Final view identified optimising the TIC index for the posterior obtained in the BBH merger simulation study."}
bbhM <- rescale(select(bbhD,-m2, -chi_eff))
if(!file.exists("cache/bbhGuidedTIC.rda")){
  set.seed(2018)
  bbhTour1 <- save_history(bbhM, guided_tour(mineIndex("TIC")))
  bbhTourFull1 <- as.list(interpolate(bbhTour1))
  save(bbhTour1, bbhTourFull1, file = "cache/bbhGuidedTIC.rda")
} else {
  load("cache/bbhGuidedTIC.rda")
}
if(!file.exists("cache/bbhGuidedSpline.rda")){
  set.seed(2018)
  bbhTour2 <- save_history(bbhM, guided_tour(splineIndex()))
  bbhTourFull2 <- as.list(interpolate(bbhTour2))
  save(bbhTour2, bbhTourFull2, file = "cache/bbhGuidedSpline.rda")
} else {
  load("cache/bbhGuidedSpline.rda")
}
if(!file.exists("cache/bbhGuidedConvex.rda")){
  set.seed(2018)
  bbhTour3 <- save_history(bbhM, guided_tour(invConvexIndex()))
  bbhTourFull3 <- as.list(interpolate(bbhTour3))
  save(bbhTour3, bbhTourFull3, file = "cache/bbhGuidedConvex.rda")
} else {
  load("cache/bbhGuidedConvex.rda")
}

iLast <- length(bbhTourFull1)
fProj1 <- bbhTourFull1[[iLast]]
dProj <- as.tibble(bbhM %*% fProj1)
p1 <- ggplot(dProj, aes(V1,V2)) + geom_point() + theme(aspect.ratio=1)
iLast <- length(bbhTourFull2)
fProj2 <- bbhTourFull2[[iLast]]
dProj <- as.tibble(bbhM %*% fProj2)
p2 <- ggplot(dProj, aes(V1,V2)) + geom_point() + theme(aspect.ratio=1)
iLast <- length(bbhTourFull3)
fProj3 <- bbhTourFull3[[iLast]]
dProj <- as.tibble(bbhM %*% fProj3)
p3 <- ggplot(dProj, aes(V1,V2)) + geom_point() + theme(aspect.ratio=1)
grid.arrange(p1, p2, p3, ncol=3) 
```
